Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-03-30 paper/paper.tex
More

We will be working with graphs which may be directed, which may have labels associated with
vertices, edges, or both, and which may contain loops. To simplify notation, we will work with a
single definition throughout: we define a \emph{graph} $G = (V, \ell, e)$ to be a set of vertices
$V$, a vertex labelling function $\ell : V \rightarrow \mathbb{N}$, and an edge labelling function
$e : V \times V \rightarrow \mathbb{N} \cup \{ \bot \}$. To represent graphs without vertex (or
edge) labels, we just pick our favourite number and give it to every vertex (or edge). We also use a
distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices.  We write
$\operatorname{V}(G)$ for $V$, and $\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood}
of a vertex $v$ (that is, the set of vertices $w$ such that either $e(v, w) \ne \bot$ or $e(w, v)
\ne \bot$).  A \emph{path} between two vertices $v$ and $w$ is a sequence of $n$ vertices $v = v_1,
v_2, \ldots, v_n = w$ such that for each $m \in \{ 1 \ldots n - 1 \}$, $e(v_m, v_{m + 1}) \ne \bot$.
A graph is \emph{connected} if a path exists between each distinct pair of vertices.

@@

@@

        \begin{scope}[xshift=15cm]
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2, 9.5) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4, 9.5) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (6, 9.5) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (8, 9.5) {\phantom{0}};
            \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
            \node [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
            \node [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
            \node [above = 0 of Ma4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb1) at (0.5, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (0.5, 4) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (0.5, 6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (0.5, 8) {\phantom{0}};
            \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
            \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2, 0.5) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mc2) at (4, 0.5) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (6, 0.5) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (8, 0.5) {\phantom{0}};
            \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
            \node [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
            \node [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
            \node [below = 0 of Mc4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9.5, 2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9.5, 4) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9.5, 6) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md4) at (9.5, 8) {\phantom{0}};
            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
            \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
            \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };

@@

    \caption{A maximum common induced subgraph between the two graphs on the left has three
        vertices---one solution is highlighted. On the right, the association graph encoding: the
    highlighted clique of size three shows the same solution.}\label{figure:association}
\end{figure}

Explain association graph. ?? cite history, connections to microstructure

@@

@@

\subsection{Edge Labels}

@@

            \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
                \stepcounter{stepcounter}\roman{stepcounter}) Forced $e \mapsto \bot$ };
        \end{scope}
    \end{tikzpicture}

@@

?? We only need to work off whichever input gives us the variables. But the constraint programming
approach seems to look at both?

@@

?? We need a picture here.

@@

>>>>

We will be working with graphs which may be directed, which may have labels associated with
vertices, edges, or both, and which may contain loops. To simplify notation, we will work with a
single definition throughout: we define a \emph{graph} $G = (V, \ell, e)$ to be a set of vertices
$V$, a vertex labelling function $\ell : V \rightarrow \mathbb{N}$, and an edge labelling function
$e : V \times V \rightarrow \mathbb{N} \cup \{ \bot \}$. To represent graphs without vertex (or
edge) labels, we just pick our favourite number and give it to every vertex (or edge). We also use a
distinct label $\bot$ to represent the \emph{lack of} an edge between two vertices.  We write
$\operatorname{V}(G)$ for $V$, and $\operatorname{N}(G, v)$ for the \emph{undirected neighbourhood}
of a vertex $v$ (that is, the set of vertices $w$ such that either $e(v, w) \ne \bot$ or $e(w, v)
\ne \bot$); a vertex is \emph{isolated} if its neighbourhood is empty. A \emph{path} between two
vertices $v$ and $w$ is a sequence of $n$ vertices $v = v_1, v_2, \ldots, v_n = w$ such that for
each $m \in \{ 1 \ldots n - 1 \}$, $e(v_m, v_{m + 1}) \ne \bot$.  A graph is \emph{connected} if a
path exists between each distinct pair of vertices.

@@

Explain association graph \cref{figure:association}, cite history, connections to microstructure
\cite{DBLP:conf/aaai/Jegou93a}.

@@

        \begin{scope}[xshift=15cm]
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma1) at (2.6, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma2) at (4.2, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma3) at (5.8, 9) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Ma4) at (7.4, 9) {\phantom{0}};
            \node [above = 0 of Ma1, font=\small] { \vphantom{0}1 };
            \node [above = 0 of Ma2, font=\small] { \vphantom{0}2 };
            \node [above = 0 of Ma3, font=\small] { \vphantom{0}3 };
            \node [above = 0 of Ma4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mb1) at (1, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb2) at (1, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb3) at (1, 5.8) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mb4) at (1, 7.4) {\phantom{0}};
            \node [left = 0 of Mb1, font=\small] { \vphantom{0}1 };
            \node [left = 0 of Mb2, font=\small] { \vphantom{0}2 };
            \node [left = 0 of Mb3, font=\small] { \vphantom{0}3 };
            \node [left = 0 of Mb4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc1) at (2.6, 1) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Mc2) at (4.2, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc3) at (5.8, 1) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Mc4) at (7.4, 1) {\phantom{0}};
            \node [below = 0 of Mc1, font=\small] { \vphantom{0}1 };
            \node [below = 0 of Mc2, font=\small] { \vphantom{0}2 };
            \node [below = 0 of Mc3, font=\small] { \vphantom{0}3 };
            \node [below = 0 of Mc4, font=\small] { \vphantom{0}4 };

@@

            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md1) at (9, 2.6) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md2) at (9, 4.2) {\phantom{0}};
            \node[draw, circle, fill=white, draw=uofgsandstone!40, inner sep=0.5pt, font=\normalsize] (Md3) at (9, 5.8) {\phantom{0}};
            \node[draw, circle, fill=uofgcobalt, inner sep=0.5pt, font=\normalsize] (Md4) at (9, 7.4) {\phantom{0}};
            \node [right = 0 of Md1, font=\small] { \vphantom{0}1 };
            \node [right = 0 of Md2, font=\small] { \vphantom{0}2 };
            \node [right = 0 of Md3, font=\small] { \vphantom{0}3 };
            \node [right = 0 of Md4, font=\small] { \vphantom{0}4 };

@@

    \caption{A maximum common induced subgraph between the two graphs on the left has three
        vertices---one solution is highlighted. On the right, the association graph encoding: the
        highlighted clique of size three shows the same solution. In practice the isolated vertices
        (corresponding to assignments between incompatible vertices, which are unary constraints) would be
        omitted.}\label{figure:association}
\end{figure}

@@

?? Break this down more by family, size, etc.

@@

\subsection{Filtering from Edge Labels}

@@

            \node [anchor=base, yshift=-2.2cm] at ($(Ma)!0.5!(M2)$) {
                \stepcounter{stepcounter}\roman{stepcounter}) $e \mapsto \bot$ is forced };
        \end{scope}
    \end{tikzpicture}

@@

@@

@@

\paragraph{By family} ?? Break this down more by family, size, etc.
